Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-02 paper/paper.tex
update code in paper

\begin{lstlisting}
case Let(x, App(f, ae), e) =>
  val closures = aeval(f, env, store).asInstanceOf[Set[Clos]]
  nd[Clos, Ans](closures, Set[VS](), { case (clos, clsacc, clsnd) =>
    val Clos(Lam(v, body), c_env) = clos
    val baddr = allocBind(v, new_time)
    val new_cenv = c_env + (v -> baddr)
    val new_store = store.update(baddr, aeval(ae, env, store))
    aeval(body, new_cenv, new_store, new_time, (bdvss: Set[VS]) => {
      nd[VS, Ans](bdvss, Set[VS](), { case (vs, bdacc, bdnd) =>
        val VS(vals, time, store) = vs
        val baddr = allocBind(x, time)
        val new_env = env + (x -> baddr)
        val new_store = store.update(baddr, vals)
        aeval(e, new_env, new_store, time, { 
          /* accumulate the values of one path, and call next body value */
          case evss => bdnd(bdacc ++ evss) 
        })
      }, { 
        /* accumulate the values of paths, and call next closure */
        case evss => clsnd(evss ++ clsacc) 
      })
    })
  },
  continue)
\end{lstlisting}

>>>>

\begin{lstlisting}
case Let(x, App(f, ae), e) =>
  val closures = aeval(f, env, store).asInstanceOf[Set[Clos]]
  nd[Clos, Ans](closures, Set[VS](), { case (clos, clsacc, clsnd) =>
    val Clos(Lam(v, body), c_env) = clos
    val baddr = allocBind(v, new_time)
    val new_cenv = c_env + (v -> baddr)
    val new_store = store.update(baddr, aeval(ae, env, store))
    aeval(body, new_cenv, new_store, new_time, (bdvss: Set[VS]) => {
      nd[VS, Ans](bdvss, Set[VS](), { case (vs, bdacc, bdnd) =>
        val VS(vals, time, store) = vs
        val baddr = allocBind(x, time)
        val new_env = env + (x -> baddr)
        val new_store = store.update(baddr, vals)
        aeval(e, new_env, new_store, time, { 
          /* accumulate the values of one path, and call next body expression of f */
          case evss => bdnd(bdacc ++ evss) 
        })
      }, { 
        /* accumulate the values of paths, and call next target closure */
        case evss => clsnd(evss ++ clsacc) 
      })
    })
  },
  continue)
\end{lstlisting}
